\chapter{Preface}
\label{Preface}
This report is the result of a project on the bachelor in Software Development at the IT-University of Copenhagen spanning from the 2nd of February 2012 to the 23rd of May 2012. \\The project was given on the second semester of the bachelor and corresponds to 15 ECTS-credits.

The project ("Software Development in Large Teams with International Collaboration") is described as centered on developing and implementing a rental service for digital media. The is goal is to develop a client-server solution backed by a relational database system. \\Students work in the teams of four to six people and collaborate and negotiate with students from Singapore Management University (SMU) in English.\\This specific project was done by five ITU students who collaborated with three SMU students.

The challenges of this projects were:
\begin{my_itemize}
\item Dealing with cultural gaps and time differences in communication with team members from Singapore.
\item Sharing a balanced amount of information to have successful collaboration.
\item Reaching agreements that both ITU and SMU students found satisfactory.
\item Conducting constructive feedback on fellow students work.
\item Constructing a client/server solution in C\#.
\end{my_itemize}
Whenever we reference the Bibliography (found on page \pageref{Biblio}), we use the signature \cite{WoT} to indicate such. \cite{WoT} refers to the link to a blog describing "The Way of Testivus".

\section{Version control repository and Scrum tracker}
\label{Preface_Trackers}
We use Git (at GitHub) as our version control system. The repository is public and can be found at \begin{my_itemize}\item github.com/itu-bswu/RentIt\end{my_itemize}

In addition, we use a free tool called Pivotal Tracker to track our user stories for the Scrum\footnote{Further detailed in our \ref{Collaboration} chapter on \pageref{Collaboration}.} development model we have chosen to use. This tool can be found at \begin{my_itemize}\item pivotaltracker.com/projects/492063\end{my_itemize}
\section{Dictionary}
\label{Preface_Dictionary}
This list describes some of the more uncommon terms we use in this report.
\begin{my_description}
\item[BugJail] If there is ever a situation where a teammember has five issues attached to them, they are placed in "BugJail" and are not allowed to work on new code until they have cleared some of the issues.
\item[Feature Freeze] We have set our feature freeze date as May 8th. After May 8th, we are not allowed to add new features to our system.
\item[Code Freeze] Our code freeze date is May 15th. After this date, we are not allowed to add code to our project (unless extremely important).
\end{my_description}