\documentclass[11pt, danish, a4paper, oneside]{report}  
\usepackage{t1enc}    % danish letters
\usepackage{babel}    % danish hyphenation
\usepackage{geometry} % page layout and A4 paper
\usepackage{graphicx}

\begin{document}

\chapter{Reflection}
\section*{Reflection}
\label{reflection}
We have, over 5 weeks of this project, worked together with a group of students from the Singaporean Management University in Singapore. We agreed with them, from the beginning, that we were to meet at least once a week to update each other on our status and to discuss what needed to be done.

During these meetings, both groups would have some ideas that were thrown around. This included odd ideas like only letting one person rent a movie at a time, effectively making it like a physical store. All the ideas were pondered by both groups, and both groups gave their input. In the end we decided to go with the ideas that both groups agreed on, and leave client-side features like Facebook integration to the client developers.

The meetings were done through the use of Google+ Hangout, which not only allowed us to speak with each other, but also see each other like in regular video conferences. We felt that it increased the quality of the meetings, and we thought that it was nice to be able to see who we were talking to. This certainly improved our communication during the meetings.

Unfortunately, it did not make us able to predict some of the ``mood changes'' that the Singaporeans had. During our meetings we'd agreed with them on something, and the next day we'd receive a mail saying ``can we do it this way instead? '', with their suggestion usually being something completely opposite of what we had agreed on. Whenever this happened, we'd end up having an email conversation with the Singaporeans, and in the end we would come to a compromise that both sides would agree on.

Unfortunately this wasn't the only problem we encountered with regards to communication. They had spent some time looking this API over before they sent us an email with questions about it, and when we received the questions we had no idea what they were talking about. Somehow, they managed to find an API that wasn't ours, and they had been looking at that one instead of ours. This lead to a bit of confusion and another mail conversation, but in the end we managed to solve the issue, and make them look at the correct API.

There was some misconception with regards to what they were capable of with regards to programming on our side. We thought that they were about our level when it came to programming, but it turned out that they weren't. This meant that some things were not done correctly on their end, which resulted in extra work for both ends, along with a lot of extra emailing between the two groups.

This is not to say that they created all the problems, as we had some problems on our side as well, problems which impacted their side. For example we had some database issues at the beginning of the project, which pretty much prevented us for developing anything for a week. The database issue put us behind schedule, and because of that, the Singaporeans were put behind schedule.

The fact that they were put behind schedule turned out to be a major problem, as they were rather slow to report when they encountered problems. Towards the end of their schedule, they were unable to make our service work for them, and they didn't tell us until they were approaching their own deadline. We managed to solve the issue, though it could have been handled a lot better and faster if we had received their report earlier. 

This also illustrates another problem that was with the communication; while communication was good during the meetings, the groups didn't really communicate much during the rest of the time. Neither group sent status emails or anything, so neither group had any idea about how the other group was doing. This became apparent when we asked for a status, but we didn't receive one. It was mainly a problem that ``belonged'' to both groups, however, as neither group really sent other emails that the ones we talked about on our weekly meetings.

To sum it all up: During the weekly meetings our communication was perfectly good, but as soon as the meeting was over, communication fell to a lower level, as both groups began to focus on other things again. This is an important lecture, that we (in the Danish group) have learned a lot from.

\end{document}