\chapter{Requirements}
\label{Requirements}

\section{Required features}
\label{Requirements_Features}

\begin{description}
\item[List movies] Be able to get a list of all movies. 
\item[Search] Be able to search for a movie title. 
\item[Browse by genre] Be able to get all genres and get all movie in a genre. 
\item[View movie details] Get details about a movie. 
\item[Download movie] Be able to download a movie. 
\item[Create user, login/logout] Be able to create a user, and be able to log in and out of the system.
\item[Upload movie] Be able to upload a movie file. 
\item[Edit movie information] Be able to edit information about a movie. 
\end{description}

\section{Optional features}
\label{Requirements_Optional}

\begin{description}
\item[Release dates] Be able to specify a release date for a movie, so that users won't be able to download a movie before.
\item[Improved search] Making the search check for spelling errors, find incomplete matches and search in movie metadata.
\item[Movie tags] Be able to attach tags to a movie for improved search results.
\item[Movie ratings] Making users able to give a rating to movies they have watched.
\item[User banning] Making admins able to ban users for various reasons.
\item[Discounts] Giving discounts on multiple movie purchases.
\item[Movie series] Being able to mark movies as in a series.
\item[Trailers] Be able to watch trailers to movies.
\item[In-app movie player] Be able to watch rented movies from within the app.
\end{description}