\chapter{Original Use Cases}
\label{Appendix_OUC}
The use cases here are the first list of use cases we agreed on with SMU. These later changed into what can be found in our \nameref{Requirements} chapter in section \ref{Requirements_UC} on page \pageref{Requirements_UC}.
\section{User account management}
\label{Appendix_OUC_UAM}
\begin{my_itemize}
\item A user is signing up for the service.
\item A user log in to the service.
\item A user edits his/her personal information.
\end{my_itemize}
\section{Media browsing}
\label{Appendix_OUC_MB}
\begin{my_itemize}
\item A user is browsing the newest added movies.
\item A user is browsing the most downloaded movies.
\item A user is browsing movies by genre.
\item A user is browsing all movies and sorts them by their name or genre.
\item A user is browsing all movies he/her previously rented.
\item A user is searching for at movie by its name.
\end{my_itemize}
\section{Media rental}
\label{Appendix_OUC_MR}
\begin{my_itemize}
\item A user is renting a movie.
\item A user is viewing information about a movie.
\end{my_itemize}
\section{Content management}
\label{Appendix_OUC_CM}
\begin{my_itemize}
\item A content manager uploads a new movie, and enters information about that movie.
\item A content manager edits information for a movie.
\item A content manager deletes a movie.
\end{my_itemize}
\section{System management (?)}
\label{Appendix_OUC_SM}
\begin{my_itemize}
\item A system manager browses all the content managers.
\item A system manager creates a new content manager.
\item A system manager deletes a content manager.
\item A system manager browses all the users.
\item A system manager deletes a user.
\end{my_itemize}